PInSoRo: A Dataset for Deep-Learning of Human-Robot Social Interactions

### 2017-06-28 paper.tex
WIP

\title{PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.9\linewidth]{3d-point-cloud-facial-features}
    \caption{The reconstructed 3D point cloud of one child face with the
    detected 68 facial features, visualised in RViz.}

@@

The experimental setup is visible in Fig.~\ref{fig|freeplay}, left.  The experimenter
stays in the room, visible to the child, during the whole experiment. When
requested by the nursery or school, another childminder (nursery/school staff)
can be present in the room. She/he is however asked not to step in during the
experiment.

@@

We recruited normally developing children, from local primary schools and
nurseries. The children are aged 4 to 8 ($M=5.8$). So far, 50 children (23
female, 27 males) were recorded in pairs. Pairs were formed by the school or
nursery staff, and all the pairs knew each other before hand.

@@

\newcommand{\tabitem}{~~\llap{\textbullet}~~}
    \begin{tabular}{@{}p{0.2\linewidth}p{0.8\linewidth}@{}}
\toprule
\bf Greetings                     & \tabitem explain the purpose of the study: showing robots how children play  \\
\emph{(about 5 min)}              & \tabitem briefly present a Nao robot: the robot stands up, gives a short
                                    message (\emph{"Hello, I'm Nao. Today, I'll be watching you while you
                                    play and soon I'll be able to play with you. Is that alright?"}), and
                                    sits down. The robot is then put aside and does not intervene
                                    for the remaining of the experiment \\
                                    %Condition B: "Hello, I'm Nao. Today I'll be playing with you. Exciting!")\\ 
                                  & \tabitem place children on cushions \\ 
                                  & \tabitem give them the yellow/purple sport
                                  bibs and make sure their hair is tied \\ 
                                  & \tabitem complete demographics on the tablet \\
                                  & \tabitem remind the children that they can withdraw at anytime \\ \midrule
        \bf Visual focus task             &  \emph{}\\ 
\emph{(30 sec)}                   &  \\ \midrule
\bf Tutorial                      & explain how to interact with the game, ensure the children are confident with the manipulation/drawing \\ 
\emph{(1-2 min)}                  &  \\ \midrule
\bf Item placement game           &  \\
\emph{(5 to 10 min)}              &  \\ \midrule
\bf Freeplay task                 & \tabitem start the recording \\
\emph{(up to 40 min)}             & \tabitem initial prompt: \emph{"Just to remind you, you can use the animals or draw. Whatever you
                                  like. If you run out of ideas, there's also an ideas box. For example, the first one is a
                                  zoo. You could draw a zoo or tell a story. When you get bored or don't want to play
                                  anymore, just let me know."} \\
                                  & \tabitem let children play \\
                                  & \tabitem once they wish to stop, stop recording \\ \midrule
\bf Debriefing                    &  \tabitem answer possible questions from the children \\
\emph{(about 2 min)}              & \tabitem give stickers as a thank you \\ \bottomrule
\end{tabular}

@@

The dataset contains the raw datastreams, as recorded during the study. No post-processing has been applied.
% in the robot condition, the interaction bag is trimmed to start once the robot is localised
While the raw RGB and depth video streams are neither rectified nor registered together (due
to performance considerations during the recording), it can be easily achieved
as a post-process step, using standard ROS tools (the ROS {\tt rgbd\_pipeline}).
Pre-configured scripts are available alongside the dataset\footnote{Available
online from
\url{https://github.com/severin-lemaignan/freeplay-sandbox-analysis}.} to
republish registered streams and the corresponding 3D point-clouds (as seen in
Fig.~\ref{fig|rviz}).

Using the {\tt gazr} face tracking library\footnote{Available online from
\url{https://github.com/severin-lemaignan/gazr}. {\tt gazr} relies on the {\tt
dlib} face tracker for facial features
extraction.}~\cite{lemaignan2016realtime}, children faces and facial features can
are extracted and reprojected onto the 3D point-clouds (Fig.~\ref{fig|rviz}). Faces have been successfully detected in 56\% of the recorded frames
in the dataset. Undetected faces are due to occlusions (a child put her arm in
front of the camera), large head rotations or quick child motion.

@@

The last part of the dataset consist in annotations of the
children's social behaviours. Some of these behaviours are automatically
computed and coded (mutual gaze, for instance), some are human-coded.
The annotations are integrated in the dataset as a timestamped datastream.

@@

We use the \emph{Social Communication Coding System} proposed by
Olswang~\etal\cite{olswang2006reliability}. It consists in 6 constructs
characterising social communication (Table~\ref{table|sccs}).

\begin{table}[]
\centering
\caption{Constructs of the Social Communication Coding System (SCCS), taken from~\cite{olswang2006reliability}}
\label{table|sccs}
\renewcommand{\arraystretch}{1.8}
\begin{tabular}{@{}lp{0.8\linewidth}@{}}
\toprule
\bf Construct          & \bf Description                                                                                                                                                                                                                                                                                                                                           \\ \midrule
Hostile/coercive   & anti-social behavior; examples include grabbing, hitting, taunting, provoking, yelling.                                                       \\
Prosocial/engaged  & engaged in a positive social interaction; examples include on-task work or conversations, helping, sharing, and compromising.                 \\
Assertive          & child stating a position or opinion; examples include asserting beliefs (verbally or nonverbally), directing the partner.                     \\
Passive/disengaged & lack of involvement in the activity, physical disengagement; examples include staring into space, putting head down, speaking quite softly, and walking away from an activity.\\
Adult seeking      & effort to seek assistance or attention from an adult; examples include requesting help.                                                       \\
Irrelevant         & child being actively engaged in an off-task behavior; examples include starting a different activity, fiddling with objects as a main focus of attention, goofy or silly behaviors. \\ \bottomrule
\end{tabular}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{analysis}
    \caption{Screenshot of the interaction analysis tool: key record information
    are played back in a synchronised (faces and audio of the two children,
    interaction occuring on the interactive table, etc.) while the human coder
    annotate the record timeline with social situations of interest.}
    \label{fig|analysis}
\end{figure}

Several metrics and coding scheme

analysis of behavioural alignment between partners (via
metrics like the recently proposed \emph{Individual Motor
Signature}~\cite{slowinski2016dynamic})

Słowinski’s Individual Motor Signature
(for behavioural alignment), Anderson's~\cite{anderson2004social} coding of children’s free-play
interactions,

>>>>

\title{PInSoRo: A Dataset for Deep-Learning of Human-Robot Social Interactions}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.9\linewidth]{3d-point-cloud-facial-features}
    \caption{The reconstructed 3D point cloud of one child face with the
    68 detected facial features, visualised in RViz.}

@@

The experimental setup is visible in Fig.~\ref{fig|freeplay}, left.  The
experimenter stays in the room, visible to the child, during the whole
experiment. When requested by the nursery or school, another childminder
(nursery/school staff) can be present in the room. She/he is however asked not
to step in during the experiment. Not pictured on Fig.~\ref{fig|freeplay} is an
'ideas box', containing 5 cards depicting simple environments (zoo, forest,
city, space, pirates).  Children are invited by the experimenter to pick up a
card whenever they run out of activity ideas.

@@

We recruited normally developing children, from local primary schools and
nurseries. The children are aged 4 to 8 ($M=5.8$). So far, 50 children (23
female, 27 males) were recorded in pairs. Pairs were formed by the school or
nursery staff, and all the pairs knew each other beforehand.

@@

\newcommand{\tabitem}{~~\llap{\textbullet}~~}
    \begin{tabular}{@{}p{0.2\linewidth}p{0.8\linewidth}@{}}
\toprule
\bf Greetings                     & \tabitem explain the purpose of the study: showing robots how children play  \\
\emph{(about 5 min)}              & \tabitem briefly present a Nao robot: the robot stands up, gives a short
                                    message (\emph{"Hello, I'm Nao. Today, I'll be watching you while you
                                    play and soon I'll be able to play with you. Is that alright?"}), and
                                    sits down. The robot is then put aside and does not intervene
                                    for the remaining of the experiment \\
                                    %Condition B: "Hello, I'm Nao. Today I'll be playing with you. Exciting!")\\ 
                                  & \tabitem place children on cushions \\ 
                                  & \tabitem give them the yellow/purple sport
                                  bibs and make sure their hair is tied \\ 
                                  & \tabitem complete demographics on the tablet \\
                                  & \tabitem remind the children that they can withdraw at anytime \\ \midrule
\bf Visual focus task             & \emph{(unrelated visual task where children gaze at a moving target)}\\ 
\emph{(30 sec)}                   & \\ \midrule
\bf Tutorial                      & explain how to interact with the game, ensure the children are confident with the manipulation/drawing \\ 
\emph{(1-2 min)}                  & \\ \midrule
\bf Items placement game          & \emph{(unrelated task on spatial reasoning -- as this task uses the same graphical environment as the main free-play task, it helps the children to familiarise themselves with the game environment)} \\
\emph{(5 to 10 min)}              &  \\ \midrule
\bf Freeplay task                 & \tabitem initial prompt: \emph{"Just to remind you, you can use the animals or draw. Whatever you
                                  like. If you run out of ideas, there's also an ideas box. For example, the first one is a
                                  zoo. You could draw a zoo or tell a story. When you get bored or don't want to play
                                  anymore, just let me know."} \\
                                  & \tabitem let children play \\
                                  & \tabitem once they wish to stop, stop recording \\ \midrule
\bf Debriefing                    &  \tabitem answer possible questions from the children \\
\emph{(about 2 min)}              & \tabitem give stickers as a thank you \\ \bottomrule
\end{tabular}

No rewards were given to the children beyond a sticker and, at the end of the
acquisition campaign, a demonstration of robots with the whole class.

@@

The dataset contains the raw datastreams, as recorded during the study.
% in the robot condition, the interaction bag is trimmed to start once the robot is localised
While the raw RGB and depth video streams are neither rectified nor registered
together (due to performance considerations during the recording), it can be
easily achieved using standard ROS tools (the ROS {\tt
rgbd\_pipeline}). Pre-configured scripts are available alongside the
dataset\footnote{Available online from
\url{https://github.com/severin-lemaignan/freeplay-sandbox-analysis}.} to
republish registered streams and the corresponding 3D point-clouds (as seen in
Fig.~\ref{fig|rviz}).

Using the {\tt gazr} face tracking library\footnote{Available online from
\url{https://github.com/severin-lemaignan/gazr}. {\tt gazr} relies on the {\tt
dlib} face tracker for facial features
extraction.}~\cite{lemaignan2016realtime}, children faces and facial features
can be extracted and reprojected onto the 3D point-clouds
(Fig.~\ref{fig|rviz}). Faces have been successfully detected in 56\% of the
recorded frames in the dataset -- undetected faces are due to occlusions (a child
put her arm in front of the camera), large head rotations or quick child
motion -- and whenever a face is present, the corresponding 3D facial features
have been added to the dataset.

@@

The last part of the dataset consist in annotations of the children's social
behaviours. These behaviours are either automatically computed and coded
(mutual gaze, for instance), or are human-coded. The annotations are all
timestamped and integrated as an independent datastream in the dataset.

@@

The dataset includes two types of manual annotations: \emph{remarkable events},
annotated by the experimenter during the experiment as free text annotation, and
\emph{social behaviours} coded with the \emph{Social Communication Coding
System} (SCCS) proposed by Olswang~\etal\cite{olswang2006reliability}.
These annotations are performed post-hoc, with a dedicated tool, able to replay synchronously
the main datastreams (Fig.~\ref{fig|analysis}).

The SCCS consists in 6 mutually exclusive constructs characterising social
communication (Table~\ref{table|sccs}). These behaviours represent a typical
classification output that a network could be trained to recognise.

\begin{table}[]
\centering
\caption{Constructs of the Social Communication Coding System (SCCS), taken from~\cite{olswang2006reliability}}
\label{table|sccs}
\renewcommand{\arraystretch}{1.8}
\begin{tabular}{@{}lp{0.8\linewidth}@{}}
\toprule
\bf Construct          & \bf Description                                                                                                                                                                                                                                                                                                                                           \\ \midrule
Hostile/coercive   & anti-social behavior; examples include grabbing, hitting, taunting, provoking, yelling.                                                       \\
Prosocial/engaged  & engaged in a positive social interaction; examples include on-task work or conversations, helping, sharing, and compromising.                 \\
Assertive          & child stating a position or opinion; examples include asserting beliefs (verbally or non-verbally), directing the partner.                     \\
Passive/disengaged & lack of involvement in the activity, physical disengagement; examples include staring into space, putting head down, speaking quite softly, and walking away from an activity.\\
Adult seeking      & effort to seek assistance or attention from an adult; examples include requesting help.                                                       \\
Irrelevant         & child being actively engaged in an off-task behavior; examples include starting a different activity, fiddling with objects as a main focus of attention, goofy or silly behaviors. \\ \bottomrule
\end{tabular}
\end{table}

\begin{figure}[b!]
    \centering
    \includegraphics[width=0.8\linewidth]{analysis}
    \caption{Screenshot of our interaction annotation tool: the recorded interaction data
    is played back synchronously (faces and audio of the two children,
    interaction occurring on the interactive table, etc.) while the human coder
    annotate the record timeline with social situations of interest.}
    \label{fig|analysis}
\end{figure}

%Several metrics and coding scheme
%
%analysis of behavioural alignment between partners (via
%metrics like the recently proposed \emph{Individual Motor
%Signature}~\cite{slowinski2016dynamic})
%
%Słowinski’s Individual Motor Signature
%(for behavioural alignment), Anderson's~\cite{anderson2004social} coding of children’s free-play
%interactions,
